\plaintitle

### 2016-09-21 drafts/labor/discussion.tex
internet, not Internet

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \cite{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern crowd work.
For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The Internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

% Arguably the Internet has made collective action on an unprecedented scale much easier.

>>>>

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern crowd work.
For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

% Arguably the internet has made collective action on an unprecedented scale much easier.

### 2016-09-21 drafts/labor/introduction.tex
internet, not Internet

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into de--contextualized, modular blocks
enables computation to hire workers at scale through open calls on the Internet~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in the work whenever their schedules allow,
with little to no awareness of the broader context of the work, and 
with (often) fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.
In this paper, we use the term on--demand work to join a pair of related phenomena:
\begin{inlinelist}
\item \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work; and
\item \textit{gig work}, typically involving platforms for one--off jobs, like driving, courier services, or administrative support.
\end{inlinelist}
The realization that complex goals can be accomplished by directing and managing crowds of workers spurred industry to flock to sites of labor
like AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g., \cite{bernsteinSoylent,vizwiz,paolacci2010running}).

>>>>

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into de--contextualized, modular blocks
enables computation to hire workers at scale through open calls on the internet~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in the work whenever their schedules allow,
with little to no awareness of the broader context of the work, and 
with (often) fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.
In this paper, we use the term on--demand work to join a pair of related phenomena:
\begin{inlinelist}
\item \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work; and
\item \textit{gig work}, typically involving platforms for one--off jobs, like driving, courier services, or administrative support.
\end{inlinelist}
The realization that complex goals can be accomplished by directing and managing crowds of workers spurred industry to flock to sites of labor
like AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g., \cite{bernsteinSoylent,vizwiz,paolacci2010running}).
